%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{verbatim}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Hyun Ryong Lee} % Your name
\address{32 Vassar St, Cambridge, MA 02139} % Your address
\address{(607) 793-6859 \\ hrlee@csail.mit.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Massachusetts Institute of Technology, Cambridge, MA} \hfill { Aug 2016 - Current} \\ 
S.M. in Computer Science \\
Advisor: Daniel Sanchez

{\bf Cornell University, Ithaca, NY} \hfill { Aug 2010 - May 2016} \\ 
B.S. in Electrical and Computer Engineering \\
Dean's List, all semesters \\
Cum. GPA: 4.22/4.3 %( 4.00/4.00 scale ) \quad    Major GPA: 4.00/4.00  \quad 

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors and Awards}

Kwanjeong Educational Foundation Fellowship \hfill {Aug 2016 - Present} \\
John G. Pertsch Prize for highest GPA in ECE class of 2016 \hfill{May 2016} \\
Best Undergraduate Poster Award, Industry-Academia Partnership Workshop \hfill { Oct 2015} \\
Tau Beta Pi \hfill { Nov 2015 - present} \\
John G. Pertsch Prize for second highest GPA in ECE class of 2016 \hfill { May 2015} \\
Eta Kappa Nu \hfill { Mar 2015 - present} 

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}

Parallel and multicore systems, distributed systems, memory and storage systems

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

S. Subramanian, M.C. Jeffrey, M. Abeydeera, {\bf H.R. Lee}, V.A. Ying, J. Emer, D. Sanchez. 
"Fractal: An Execution Model for Fine-Grain Nested Speculative Parallelism,"
In \textit{Proc. of the 44th annual International Symposium in Computer Architecture (ISCA-44)}, June 2017

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORKSHOPS AND PRESENTATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Workshops}

J. Mukundan, J.B. Kuang, A. Jagmohan, M. Franceschini, H. Hunter, {\bf H. R. Lee}, S. Bisht, J.F. Martínez. "Improving I/O Scheduling in FLASH-based SSDs through Foresight". Industry-Academia Partnership Workshop, October 2015.

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Apple Inc.}{May 2015 - Aug 2015}{Firmware Engineering Intern}{Cupertino, CA}

\item Refactored the C firmware codebase of Mac related input devices to be compatible with the Clang/LLVM compiler toolchain. 
\end{rSubsection}

\begin{rSubsection}{Ministry of National Defense}{Sep 2012 - Jun 2014}{Sergeant}{Seoul, South Korea}

\item Completed two years of mandatory military service for South Korea
\end{rSubsection}

\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
%	PRIOR RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Prior Research Experience}

\begin{rSubsection}{Improving I/O Scheduling in Flash-based SSDs through Foresight}{Aug 2014 - May 2016}{Advisor: José F. Martínez}

\item Developed a self-optimizing SSD I/O scheduler based on reinforcement learning (RL) principles. 
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}

Grader, ECE 4740: Digital VLSI \hfill {Jan 2016 - May 2016} \\
Grader, ECE 2200: Signals and Systems \hfill {Jan 2015 - May 2015} \\
Grader, ECE 2300: Digital Logic Design and Computer Organization \hfill{Jan 2012 - May 2012}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
